---
title: "EFSA Submission v2"
subtitle: "Data export mapping for the FHF marine sediment data model"
---

```{css, echo=FALSE}
th {
  white-space: nowrap;
}
```

The page presents the mapping between the pilot database fields and the [EFSA Format v2](efsa-format-v2.qmd) columns.

```{r}
library(dplyr)
library(tibble)

efsa_submission_v2 <- tribble(
  ~Column,              ~Optionality,    ~`Source Table`,   ~`Source Columns`,                       ~`Fixed Text`,  ~Missing, ~Notes,
  "sampleId",           "Recommended",   "Sample",          "cruise_id + core_id + sample_id",       NA,             NA,       NA,
  "samplingStrategy",   "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "pristine",           "Mandatory",     NA,                NA,                                      "yes",          NA,       NA,
  "collDate",           "Mandatory",     "Cruise",          "start_year + start_month + start_day",  NA,             NA,       NA,
  "placeColl",          "Mandatory",     "Core",            "sea_name",                              NA,             NA,       NA,
  "lat",                "Recommended",   "Core",            "ddn",                                   NA,             NA,       NA,
  "lon",                "Recommended",   "Core",            "dde",                                   NA,             NA,       NA,
  "sedDepth",           "Mandatory",     "Sample",          "depth_from + depth_to",                 NA,             NA,       "Derived: map intervals to 0-5cm / 5-40cm / >40cm categories",
  "traceEl",            "Mandatory",     "Parameter",       "element",                               NA,             NA,       NA,
  "value",              "Mandatory",     "Sediment",        "value",                                 NA,             NA,       NA,
  "sd",                 "Optional",      NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "unit",               "Mandatory",     "Parameter",       "unit",                                  NA,             NA,       NA,
  "resultType",         "Recommended",   NA,                NA,                                      "dry weight",   NA,       NA,
  "moisture",           "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "convertedValue",     "Mandatory",     "Sediment",        "value",                                 NA,             NA,       "Values are already in mg/kg dry weight",
  "extractionClass",    "Mandatory",     "Parameter",       "method1",                               NA,             NA,       "Derived: map analytical method to extraction class",
  "methAn",             "Mandatory",     "Parameter",       "method1",                               NA,             NA,       NA,
  "validatedMethod",    "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "LOD",                "Mandatory",     "LLD",             "value",                                 NA,             NA,       NA,
  "LODUnit",            "Mandatory",     "Parameter",       "unit",                                  NA,             NA,       "Same unit as the measured value",
  "LOQ",                "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "LOQUnit",            "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "accLab",             "Mandatory",     NA,                NA,                                      "No",           NA,       NA,
  "phSed",              "Optional",      NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "sieve",              "Mandatory",     NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "bulkAnalysis",       "Mandatory",     NA,                NA,                                      NA,             "Yes",    "Not recorded in DB",
  "ocSed",              "Mandatory",     "Sediment",        "value",                                 NA,             NA,       "TOC% parameter",
  "notes",              "Recommended",   NA,                NA,                                      NA,             "Yes",    "Not recorded in DB"
)

efsa_submission_v2 <- efsa_submission_v2 %>%
  mutate(across(where(is.character), ~coalesce(.x, "")))
```

## Data Mapping for Submission

```{r}
efsa_submission_v2 %>%
  filter(Missing != "Yes") %>%
  select(-Missing)
```

## Full Data Mapping

```{r}
efsa_submission_v2
```

## Data Export Method

As the submission tool is an Excel file, the data must be mapped column by column rather than through a standard row-based export. This approach ensures that the structure of the submission file is not disrupted.
